Response to Pachter’s Review

### 2020-01-23 index.Rmd
revision

Last Update: January 23rd 2:50 A.M.

@@

So it is clear that Pachter's analysis was some sort of magic trick, potentially a thought experiment, and a fraudulent one. It is highly unlikely that a tenured and respected expert in computation and statistics did not know the above result, expecially when a student he suggests take an introductory statistics course immediately spotted it. We claim and assert that he purposefully chose his 36 cutoff to try to undermine our results.

>>>>

Last Update: January 23rd 3:16 A.M. G.M.T.

@@

So it is clear that Pachter's analysis was some sort of magic trick, potentially a thought experiment, and a misleading one. It is highly unlikely that a tenured and respected expert in computation and statistics did not know the above result, expecially when a student he suggests take an introductory statistics course immediately spotted it. One may suspect that he purposefully chose his 36 cutoff to try to undermine our results.
